Modular Synthesis of Verified Verifiers of Computation with STV Algorithms

### 2019-03-15 paper/paper.tex

 tactics for discharging proof obligations on assertions involving list structure and operations on it. This significantly eases the process of verification. 

@@

Implementing piles in this way enables us to tailor the semantics of the transfer and elect transitions and their instantiations in such a way to modularly formalise several STV schemes which use the last parcel or stepwise distribution of votes form eliminated candidates or the combination of both.

There is also a reason for choosing the type $rat$  
%as the underlying arithmetic for the formalisation, 
instead of e.g. floating numbers. Elections with an STV counting scheme have a small margin of victory especially for the last vacancy left to fill \cite{MBlo}. This margin may happen to be less than the magnitude of the error caused by the accumulation of rounding errors as it is with floating points.  Hence one must sensibly avoid the high cost of electing a wrong candidate by falling into traps of imprecise calculations due to unintelligent choices. Using exact fractions allows safe handling of calculations. 
\subsection{The Semantics and its Auxiliary Components}
\label{sec:MachineSem}

@@

Also there are some \emph{implicit} conditions present in legal documents describing transfer-elected. These constraints come to attention either as the result of a straightforward understanding of the explicit conditions above or as   auxiliary components that are taken for granted by legislators but are
necessary for proper functioning of the explicit constraints;
\begin{enumerate}
\item every candidate in the pre- and post-state of transfer-elected has a unique tally and pile
\item no one is elected or eliminated by applying transfer-elected
\item no candidate attracts any new vote by transfer-elect and therefore tallies remain the same
\item candidates whose names appear in the backlog of elected are indeed among elected candidates
\item any elected candidate is no longer a continuing candidate so that they do not receive votes any further
\item the list of competing candidates in the election is not empty and has no duplication of names
\end{enumerate}  
Conjunctions of formal declarations of the above explicit and implicit conditions form the semantics of the transition label transfer-elected.   The predicate TransferAuxSpec defines the semantics of this transition.
 \begin{small}
\begin{holthmenv}
  \HOLConst{TransferAuxSpec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;\HOLFreeVar{ba}\;\HOLFreeVar{t}\;\HOLFreeVar{t\sp{\prime}}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{bl}\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLFreeVar{e}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{\HOLTokenEquiv{}}\\
\;\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenNotEqual{}}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{t\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{e\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{length}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{st}\;\HOLSymConst{\HOLTokenConj{}}\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{t}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\\\;\;\HOLConst{ValidInitCandList}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}
\;\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{p})
\end{holthmenv}
\end{small}

Transfer-elected, as is the case for other formalised transitions, is parametrised by the quota $qu$, the number of initial vacancies $st$ and the list $l$ of all candidates competing in the election. The semantics of the transition declares that given the ballots $ba$, tally $t$, pile $p$, backlog of elected $bl$, backlog of eliminated $bl_{2}$ and the list of elected $e$ and continuing candidates $h$ in the pre-state of transfer-elected, and their respective counterparts in the post-state characterised by having a prime symbol, some conditions as specified above are satisfied by the transition.  Note that \textsf{mem} in Definition of TransferAuxSpec declares list membership.

@@

validate according to specific instances of STV. 

@@

\begin{small}
\begin{holthmenv}
  \HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{\HOLConst{mem}}\;(\HOLFreeVar{c}\HOLSymConst{,}\HOLFreeVar{x})\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{getCandTally}\;\HOLFreeVar{c}\;\HOLFreeVar{t}\;\HOLSymConst{=}\;\HOLFreeVar{x}
\end{holthmenv}
\end{small}
Using this function, we implement another function lessThanQuota which checks if the tally of every candidate in a given list $ls$ is below the quota (Item $\bullet_{1}$).
\begin{small}
\begin{holthmenv}
 \HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;\HOLFreeVar{l}\;\HOLFreeVar{ls}\;\HOLSymConst{\HOLTokenEquiv{}}\;\HOLConst{EVERY}\;(\HOLTokenLambda{}\HOLBoundVar{h}.\;\HOLConst{getCandTally}\;\HOLBoundVar{h}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu})\;\HOLFreeVar{ls}
\end{holthmenv}
\end{small} 
We show that the function lessThanQuota is a  computational realisation of  its specification: 
\begin{small}
\begin{holthmenv}
  (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{x}.\;\HOLConst{\HOLConst{mem}}\;(\HOLBoundVar{c}\HOLSymConst{,}\HOLBoundVar{x})\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLBoundVar{x}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\\
(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c\sp{\prime\prime}}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c\sp{\prime\prime}}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c\sp{\prime\prime}}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t}))\;\HOLSymConst{\HOLTokenImp{}}
\;\HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;\HOLFreeVar{t}\;\HOLFreeVar{h}
\end{holthmenv}
\end{small}
Moreover lessThanQuota enforces its specification.
 \begin{small}
\begin{holthmenv}
  \HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally_dec2}\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\\
\;\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{x}.\;\HOLConst{\HOLConst{mem}}\;(\HOLBoundVar{c}\HOLSymConst{,}\HOLBoundVar{x})\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLBoundVar{x}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu}
\end{holthmenv}
\end{small}
 In the same manner we define and verify other functions that computationally  implement the rest of components of the transfer-elected specification. Conjunctions of the implementations constitute a computational semantics for transfer-elected.

>>>>

 tactics for discharging proof obligations on assertions involving list structure and operations on it. This notably eases the verification phase. 

@@

Implementing piles in this way enables us to tailor the semantics of the transfer and elect transitions and their instantiations in such a way to modularly formalise several STV schemes which use the last parcel or stepwise distribution of votes from eliminated candidates or the combination of both.

There is also a reason for choosing the type $rat$  
%as the underlying arithmetic for the formalisation, 
instead of e.g. floating numbers. Elections with an STV counting scheme have a small margin of victory especially for the last vacancy left to fill \cite{MBlo}. This margin may happen to be less than the magnitude of error caused by the accumulation of rounding errors as it is with floating points.  Hence one must sensibly avoid the high cost of electing a wrong candidate by falling into traps of imprecise calculations due to unintelligent choices. Using exact fractions allows safe handling of calculations. 
\subsection{The Semantics and its Auxiliary Components}
\label{sec:MachineSem}

@@

Also there are some \emph{implicit} conditions present in legal documents describing transfer-elected. These constraints come to attention either as the result of a straightforward understanding of the explicit conditions above or as   auxiliary components that are taken for granted by legislators but are
necessary for proper functioning of the explicit constraints;
\begin{enumerate}
\item every candidate in the pre- and post-state of transfer-elected has a unique tally and pile
\item no one is elected or eliminated by applying transfer-elect
\item no candidate attracts any new vote by transfer-elect and therefore tallies remain the same
\item candidates whose names appear in the backlog of elected are indeed among elected candidates
\item any elected candidate is no longer a continuing candidate so that they do not receive votes any further
\item the list of competing candidates in the election is not empty and has no duplication of names
\end{enumerate}  
Conjunctions of formal declarations of the above explicit and implicit conditions form the semantics of the transition label transfer-elected.   The predicate TransferAuxSpec defines the semantics of this transition.
 \begin{small}
\begin{holthmenv}
  \HOLConst{TransferAuxSpec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;\HOLFreeVar{ba}\;\HOLFreeVar{t}\;\HOLFreeVar{t\sp{\prime}}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{bl}\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLFreeVar{e}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{\HOLTokenEquiv{}}\\
\;\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenNotEqual{}}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{t\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{e\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{length}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{st}\;\HOLSymConst{\HOLTokenConj{}}\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{t}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\\\;\;\HOLConst{ValidInitCandList}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}
\;\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{p})
\end{holthmenv}
\end{small}

Transfer-elected, 
%as is the case for 
 similar to other formalised transitions, is parametrised by the quota $qu$, the number of initial vacancies $st$ and the list $l$ of all candidates competing in the election. The semantics of the transition declares that given the ballots $ba$, tally $t$, pile $p$, backlog of elected $bl$, backlog of eliminated $bl_{2}$ and the list of elected $e$ and continuing candidates $h$ in the pre-state of transfer-elected, and their respective counterparts in the post-state characterised by having a prime symbol, some conditions as specified above are satisfied by the transition.  Note that \textsf{mem} in TransferAuxSpec declares list membership.

@@

validate according to which specific instances of STV  

@@

\begin{small}
\begin{holthmenv}
  \HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{\HOLConst{mem}}\;(\HOLFreeVar{c}\HOLSymConst{,}\HOLFreeVar{x})\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{getCandTally}\;\HOLFreeVar{c}\;\HOLFreeVar{t}\;\HOLSymConst{=}\;\HOLFreeVar{x}
\end{holthmenv}
\end{small}
Using this function, we implement another function lessThanQuota which checks if the tally of every candidate in a given list $ls$ is below the quota (Item $\bullet_{1}$).
\begin{small}
\begin{holthmenv}
 \HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;\HOLFreeVar{l}\;\HOLFreeVar{ls}\;\HOLSymConst{\HOLTokenEquiv{}}\;\HOLConst{every}\;(\HOLTokenLambda{}\HOLBoundVar{h}.\;\HOLConst{getCandTally}\;\HOLBoundVar{h}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu})\;\HOLFreeVar{ls}
\end{holthmenv}
\end{small} 
We show that the function lessThanQuota is a  computational realisation of  its specification: 
\begin{small}
\begin{holthmenv}
  (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{x}.\;\HOLConst{\HOLConst{mem}}\;(\HOLBoundVar{c}\HOLSymConst{,}\HOLBoundVar{x})\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLBoundVar{x}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\\
(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c\sp{\prime\prime}}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c\sp{\prime\prime}}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c\sp{\prime\prime}}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t}))\;\HOLSymConst{\HOLTokenImp{}}
\;\HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;\HOLFreeVar{t}\;\HOLFreeVar{h}
\end{holthmenv}
\end{small}
Moreover lessThanQuota enforces its specification.
 \begin{small}
\begin{holthmenv}
  \HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally_dec2}\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\\
\;\;\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{c}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{x}.\;\HOLConst{\HOLConst{mem}}\;(\HOLBoundVar{c}\HOLSymConst{,}\HOLBoundVar{x})\;(\HOLFreeVar{t\sb{\mathrm{0}}}\HOLSymConst{::}\HOLFreeVar{t\sb{\mathrm{1}}})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLBoundVar{x}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{qu}
\end{holthmenv}
\end{small}
 In the same manner we define and verify other functions that computationally  implement the rest of components of the transfer-elected specification. Conjunctions of the implementations constitute a computational semantics for transfer-elected.

 \begin{small}
 \begin{holthmenv}
  \HOLConst{TransferActDec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;(\HOLConst{NonFinal}\;(\HOLFreeVar{ba}\HOLSymConst{,}\HOLFreeVar{t}\HOLSymConst{,}\HOLFreeVar{p}\HOLSymConst{,}\HOLFreeVar{bl}\HOLSymConst{,}\HOLFreeVar{bl\sb{\mathrm{2}}}\HOLSymConst{,}\HOLFreeVar{e}\HOLSymConst{,}\HOLFreeVar{h}))\\
\;\;(\HOLConst{NonFinal}\;(\HOLFreeVar{ba\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{t\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{p\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{bl\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{e\sp{\prime}}\HOLSymConst{,}\HOLFreeVar{h\sp{\prime}}))\;\HOLSymConst{\HOLTokenEquiv{}}\\
\;\;\HOLConst{TransferAuxDec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;\HOLFreeVar{ba}\;\HOLFreeVar{t}\;\HOLFreeVar{t\sp{\prime}}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{bl}\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLFreeVar{e}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLConst{lessThanQuota}\;\HOLFreeVar{qu}\;\HOLFreeVar{t}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;dtcase\;\HOLFreeVar{bl}\;\HOLKeyword{of}\\
\;\;\;\;\HOLConst{\ensuremath{[\,]}}\;\HOLTokenImp{}\;\HOLConst{false}\\
\;\;\HOLTokenBar{}\;\HOLBoundVar{hbl}\HOLSymConst{::}\HOLBoundVar{tbl}\;\HOLTokenImp{}
\;(\HOLKeyword{let}\;\HOLBoundVar{gcp}\;=\;\HOLConst{getCandPile}\;\HOLBoundVar{hbl}\;\HOLFreeVar{p}\;\HOLKeyword{in}\\
\;\;\;\;\;\;\;\HOLSymConst{\HOLTokenNeg{}}\HOLConst{null}\;\HOLBoundVar{gcp}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{hbl}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sp{\prime}}\;\HOLSymConst{=}\;\HOLBoundVar{tbl}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{last}\;\HOLBoundVar{gcp}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\;\;\;\;\;\HOLConst{\HOLConst{mem}}\;(\HOLBoundVar{hbl}\HOLSymConst{,}\HOLConst{\ensuremath{[\,]}})\;\HOLFreeVar{p\sp{\prime}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{subpile1}\;\HOLBoundVar{hbl}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{subpile2}\;\HOLBoundVar{hbl}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{p})\\
\HOLConst{TransferActDec}\;\HOLFreeVar{v\sb{\mathrm{0}}}\;(\HOLConst{Final}\;\HOLFreeVar{v\sb{\mathrm{1}}})\;\HOLFreeVar{v\sb{\mathrm{2}}}\;\HOLSymConst{\HOLTokenEquiv{}}\;\HOLConst{false}\\
\HOLConst{TransferActDec}\;\HOLFreeVar{v\sb{\mathrm{3}}}\;(\HOLConst{NonFinal}\;\HOLFreeVar{v\sb{\mathrm{9}}})\;(\HOLConst{Final}\;\HOLFreeVar{v\sb{\mathrm{5}}})\;\HOLSymConst{\HOLTokenEquiv{}}\;\HOLConst{false}
\end{holthmenv}
\end{small}
The functions subpile1 and subplie2 together implement the lines marked by the star symbol in Definition of the TransferActSpec. We next demonstrate how the framework modularly extends to instantiations  with various STV algorithms.
\subsection{Variations in Instantiation}
To exemplify the flexibility of our framework, we discuss an instantiation of the machine with the CADE STV as well. We refer the reader to our source code\footnote{ see  \url{https://github.com/MiladKetabGhale/Modular_Checker}} for details of five other STV instances for which we have successfully completed the verifiers' synthesis process. 
%We have already completed the verifiers synthesis process for five different STV algorithms\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}}. Here,  we only discuss instantiation of the transfer-elect  based on the  CADE STV~\cite{cade}.
As we have already illustrated how a specification and the corresponding implementation of an algorithm advance, we therefore only elaborate on how CADE STV varies from ACT STV in textual descriptions of its  semantics and subsequently its implementations.
